---
title: "Impact of Network Difficulty on Transaction Costs for Miners"
author: "Casey Moser"
date: "6/11/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Try running data back to further (maximizee length of data), keep both but add another

# Change cost variable label to be revenue per transaction for miners

```{r}
library(tidyverse)
library(ggplot2)
library(runjags)
library(ProbBayes)
```

## 2020-2021 Analysis

# Data files

```{r}
cost<- read.csv("cost-per-transaction.csv")
fees<- read.csv("fees-usd-per-transaction.csv")
revenue<- read.csv("miners-revenue.csv")
difficulty<- read.csv("difficulty.csv")
price<- read.csv("market-price.csv")


```


```{r}
cost_difficulty <- cost %>%
left_join(difficulty) %>%
select(difficulty, cost.per.transaction, Timestamp)

```

Missing values were removed from the model.

```{r}

cost_difficulty <- cost_difficulty %>%
  na_if("") %>%
  na.omit

head(cost_difficulty)

```

# Linear Model of User Cost and Difficulty

The model below outlines the relationship of the difficulty of mining a new block for the bitcoin blockchain on the miners' revenue per bitcoin transaction.



```{r}
fit_1 <- lm(cost.per.transaction ~ difficulty,  data = cost_difficulty)

summary(fit_1)
```

Based on this linear model, a 1 unit increase in difficulty of expanding the blockchain network is correlated with a 2.247e-11 increase in mining revenue per transaction holding all other variables constant.

```{r}
ggplot(data = cost_difficulty, aes(x = difficulty, y = cost.per.transaction)) + geom_text(label= cost_difficulty$Timestamp, size=3, check_overlap = TRUE)+
geom_point(size=0.5)+geom_smooth()
```

After conducting a plot of the cost and difficulty data, there is reason to believe that the model is possibly quadratic as opposed to linear.

```{r}
cost_difficulty<-cost_difficulty %>% 
mutate(difficulty_sq= difficulty^2)
```

```{r}
fit_1_sq <- lm(cost.per.transaction ~ difficulty_sq,  data = cost_difficulty)

summary(fit_1_sq)
```


```{r}
AIC(fit_1)
AIC(fit_1_sq)
```


Since the AIC is lower on the linear model than the quadratic model,  the linear model is the better fitting model and will be used instead of the quadratic model.




Based on this model, a 1 unit increase in network difficulty is predicted to result in a 2.271e-11 increase in transaction costs for miners holding all other variables constant. Considering that network difficulty is measured in the trillions, this superficially low coefficient means that increase in network difficulty could have significant impact on mining costs for users. For example, the 4.437 trillion increase in network difficulty that occurred between May 11 and May 12 of 2021 is estimated to have caused a 100.76 USD increase in cost per transaction for users (meaning a 100.76 USD increase in mining revenue per transaction).


```{r}
25.046-20.609
(2.271e-11)*(4.437*1000000000000)
```




## All-time analysis



# Data files

```{r}
cost<- read.csv("cost-per-transaction_all.csv")
fees<- read.csv("fees-usd-per-transaction_all.csv")
revenue<- read.csv("miners-revenue_all.csv")
difficulty<- read.csv("difficulty_all.csv")
price<- read.csv("market-price_all.csv")


```




```{r}
cost_difficulty_all <- cost %>%
full_join(difficulty) %>%
select(difficulty, cost.per.transaction, Timestamp)



head(cost_difficulty_all)


```

```{r}
cost_difficulty_all <- cost_difficulty_all %>%
arrange(Timestamp)

head(cost_difficulty_all)

```

```{r}

ind <- which(is.na(cost_difficulty_all$difficulty))
cost_difficulty_all$difficulty[ind] <- sapply(ind, function(i) with(cost_difficulty_all, mean(c(difficulty[i-1], difficulty[i+1]))))

head(cost_difficulty_all)


```

```{r}
ind <- which(is.na(cost_difficulty_all$cost.per.transaction))
cost_difficulty_all$cost.per.transaction[ind] <- sapply(ind, function(i) with(cost_difficulty_all, mean(c(cost.per.transaction[i-1], cost.per.transaction[i+1]))))

tail(cost_difficulty_all)

```


```{r}

cost_difficulty_all <- cost_difficulty_all %>%
  na_if("") %>%
  na.omit

head(cost_difficulty_all)

```

```{r}
cost_difficulty_all<-cost_difficulty_all %>% 
  
rename(revenue.per.transaction = cost.per.transaction)

head(cost_difficulty_all)

```



#  Model of Cost and Difficulty for all data points

The model below outlines the relationship of the difficulty of mining a new block for the bitcoin blockchain on the miners' revenue per bitcoin transaction.

```{r}
ggplot(data = cost_difficulty_all, aes(x = difficulty, y = revenue.per.transaction)) + geom_text(label= cost_difficulty_all$Timestamp, size=3, check_overlap = TRUE)+
geom_point(size=0.5) +geom_smooth()
```

```{r}
cost_difficulty_all<- cost_difficulty_all %>% 
mutate(difficulty_sq= difficulty^2) %>% 
mutate(difficulty_cu= difficulty^3) %>% 
  mutate(difficulty_4th= difficulty^4) %>% 
   mutate(difficulty_5th= difficulty^5)

```


```{r}
fit_2 <- lm(revenue.per.transaction ~ difficulty,  data = cost_difficulty_all)

summary(fit_2)
```

```{r}
cost_difficulty_all<-cost_difficulty_all %>% 
mutate(difficulty_sq= difficulty^2) %>% 
mutate(difficulty_cu= difficulty^3) %>% 
  mutate(difficulty_4th= difficulty^4) %>% 
   mutate(difficulty_5th= difficulty^5)
```

```{r}
fit_2_sq <- lm(revenue.per.transaction ~ difficulty_sq + difficulty,  data = cost_difficulty_all)

summary(fit_2_sq)
```

```{r}
fit_2_cu <- lm(revenue.per.transaction ~ difficulty_cu + difficulty_sq + difficulty,  data = cost_difficulty_all)

summary(fit_2_cu)
```

```{r}
fit_2_4th <- lm(revenue.per.transaction ~ difficulty_4th + difficulty_cu + difficulty_sq + difficulty,  data = cost_difficulty_all)

summary(fit_2_4th)
```

```{r}
fit_2_5th <- lm(revenue.per.transaction ~ difficulty_5th + difficulty_4th + difficulty_cu + difficulty_sq + difficulty,  data = cost_difficulty_all)

summary(fit_2_5th)
```

```{r}
AIC(fit_2)
AIC(fit_2_sq)
AIC(fit_2_cu)
AIC(fit_2_4th)
AIC(fit_2_5th)

```

4th power polynomial model appears to be better fitting since it has the lowest AIC value. Considering that the AIC values for the 4th and 5th power model are so similar, I will err on the side of parsimony and choose the 4th power polynomial model.



# Inflection Points


```{r}
# coefficient for 4th power term for first derivative
(-5.850e-51)*4

# coefficient for cubic term for first derivative
( 3.417e-37)*3 

# coefficient for quadratic term for first derivative

(-5.895e-24)*2

```


# First derivative
dy/dx= -2.34e-50*x^3 +  1.0251e-36*x^2 -1.179e-23*x +  3.310e-11

# Second derivative

```{r}

# coefficient for cubic term of second derivative
(-2.34e-50)*3

# coefficient for quadratic term of second derivative
(1.0251e-36)*2 


```

-7.02e-50*x^2 + 2.0502e-36*x -1.179e-23

# Setting setting derivative=0 to find the inflection point of the curve

0= -7.02e-50*x^2 + 2.0502e-36*x -1.179e-23

```{r}

quadraticRoots <- function(a, b, c) {

  print(paste0("You have chosen the quadratic equation ", a, "x^2 + ", b, "x + ", c, "."))

  discriminant <- (b^2) - (4*a*c)

  if(discriminant < 0) {
    return(paste0("This quadratic equation has no real numbered roots."))
  }
  else if(discriminant > 0) {
    x_int_plus <- (-b + sqrt(discriminant)) / (2*a)
    x_int_neg <- (-b - sqrt(discriminant)) / (2*a)

    return(paste0("The two x-intercepts for the quadratic equation are ",
                  format(round(x_int_plus, 5), nsmall = 5), " and ",
                  format(round(x_int_neg, 5), nsmall = 5), "."))
  }
  else #discriminant = 0  case
    x_int <- (-b) / (2*a)
    return(paste0("The quadratic equation has only one root. This root is ",
                  x_int))
}

```

```{r}

quadraticRoots(-7.02e-50, 2.0502e-36, -1.179e-23 )

```
inflection points are at  7.873065e+12 and 2.133206e+13

# Log analysis


```{r}
cost_difficulty_all <- cost_difficulty_all %>%

  mutate(log_diff= log(difficulty)) %>% 

mutate(log_rev= log(revenue.per.transaction))

```

```{r}

cost_difficulty_all <- cost_difficulty_all %>%
  na_if("-Inf") %>%
  na.omit
head(cost_difficulty_all)


```
```{r}
ggplot(data = cost_difficulty_all, aes(x = log_diff, y =log_rev )) + geom_text(label= cost_difficulty_all$Timestamp, size=2, check_overlap = TRUE)+
geom_point(size=0.5) +geom_smooth()
```
```{r}
cost_difficulty_all<- cost_difficulty_all %>% 
mutate(log_diff_sq=log_diff^2)
```




```{r}
fit_log <- lm(log_rev ~ log_diff,  data = cost_difficulty_all)



summary(fit_log)

```
# Relationship between miner transaction revenue and difficulty

Based on this double log model, a 1% increase in difficulty is approximately related to a 13.37% increase in revenue per transaction.




# Predictive Model



# USE THIS CODE TO FIX THE OTHER MODELS

```{r}
library(tidyverse)
library(lubridate)
cost_difficulty_all<-cost_difficulty_all %>%
  mutate(
    Date = ymd_hms(Timestamp),
    Year= decimal_date(Date)
   


  )



head(cost_difficulty_all)

```







```{r}
ggplot(data = cost_difficulty_all, aes(x = Year, y =difficulty ))+
geom_point(size=0.5)+geom_smooth()
```


```{r}
base<-cost_difficulty_all$Year[1]
library(dplyr)
cost_difficulty_all<-cost_difficulty_all %>% 
  mutate(Time= Year-base )



```

```{r}
ggplot(data = cost_difficulty_all, aes(x = Time, y =difficulty ))+
geom_point(size=0.5)+geom_smooth()
```

```{r}
cost_difficulty_all<-cost_difficulty_all %>% 
  mutate(Time_exp=exp(Time))
```


```{r}
fit_time <- lm(difficulty ~  Time+Time_exp,  data = cost_difficulty_all)

summary(fit_time)
```



```{r}
# Prediction for 2121
predict_df <- data.frame(Time= 111) %>% 
  mutate(Time_exp=exp(Time))
 diff_2121<-predict(fit_time, predict_df, type = "response")
```

# Logistic Model Prediction

```{r}
predict_df <- data.frame(difficulty= diff_2121)%>%
mutate(log_diff = log(difficulty)) 


 log_pred<- predict(fit_log, predict_df, type = "response")
 
 exp(log_pred)
```



Based on the logistic model, the predicted revenue per transaction for miners is $43676021




